A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-28 paper/ms.tex
update ms (LAH init comments)
Co-authored-by: Lynne Hillenbrand <lah@astro.caltech.edu>

%\suppressAffiliations
\NewPageAfterKeywords
\input{authors.tex}

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.4\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge,
  Kepler\,1627Ab is the youngest planet with a precise age yet found
  by the main Kepler mission.  The Kepler data show two notable
  anomalies: the average Kepler transit profile appears to be
  asymmetric, and the individual transits show a correlation between
  the transit time and the local slope of the light curve.  The former
  might be explained by a dusty atmospheric outflow; the latter could
  be explained by unresolved starspot crossings of a planet on a
  prograde orbit.  Broadly speaking, the $\delta$~Lyr cluster is one
  of many stellar groups whose properties have been clarified using
  Gaia; many other exoplanet hosts belong to these new clusters.
  Verifying the results of Gaia clustering analyses using TESS
  rotation periods offers a promising path toward expanding the census
  of age-dated planets, and our corresponding understanding of
  planetary evolution.
\end{abstract}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler's view of the $\delta$~Lyr cluster.} Each black circle is a
    candidate cluster member, selected from the catalog of \citet{KounkelCovey2019} based on its
    position and kinematics (see Appendix~\ref{app:kinematicselection}).
    Of the \nkinematic\ candidate cluster members, 58 have at least one
    quarter of Kepler data.  TESS has also observed most of the
    cluster, for one to two lunar months to date.
		\label{fig:skychart}
	}
\end{figure}

Matching our young star list against stars observed by Kepler yielded
two discoveries.  The first, to be discussed in an upcoming analysis
by J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr
open cluster Theia~520 (UBC~1).  At least six Kepler planets are known
in the cluster from the Kepler-52 and Kepler-968 systems
\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
discovery, and the focus of this work, is that Kepler observed a
portion of the $\delta$\,Lyr cluster (Stephenson-1; Theia~73;
\citealt{stephenson_possible_1959}).  Figure~\ref{fig:skychart} shows
the overlap between the Kepler field and the cluster.

A previous clustering analysis of the Gaia data reported that
Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a member of the
\cn\ \citep{kounkel_untangling_2019}.  Given the previous statistical
validation of the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and that \sn\ is indeed a member of the
cluster.  Focusing on the planet itself, we confirm that despite the
presence of a previously unreported binary companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A (Section~\ref{sec:planet}).
Based on a correlation between the planetary transit times and the local
light curve slope, the orbit also seems to be prograde.  We
conclude by highlighting broader implications for our ability to
age-date a larger sample of planets (Section~\ref{sec:conc}).

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f2c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is \clusterage\ old.}  {\it Top:} Color-absolute
    magnitude diagram of candidate \cn\ members, in addition to stars
    in IC\,2602 ($\approx38$\,Myr), the Pleiades ($\approx 115$\,Myr;
    \citealt{dahm_2015}), and the Gaia EDR3 Catalog of Nearby Stars
    (gray background).  The zoomed right panel highlights the
    pre-main-sequence.  The \cn\ and IC\,2602 are approximately the
    same isochronal age.  {\it Bottom:} TESS and Kepler stellar
    rotation period versus dereddened Gaia color, with the Pleiades
    and Praesepe (650\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.  Most candidate
    \cn\ members are gyrochronally younger than the Pleiades; outliers
    are probably field interlopers.
   \label{fig:age}
	}
\end{figure*}

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades,
and a 16\,Myr age for UCL \citep{dahm_2015,pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,dobbie_ic_2010,david_ages_2015,randich_gaiaeso_2018,bossini_age_2019,bouma_cluster_2020}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse extreme of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age for IC\,2602, which yields an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST isochrone
models over a grid of ages, metallicities, and reddenings, yielded the
best agreement for this $\approx 38\,$Myr age as well, given ${\rm
[Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CAMD
reddening is higher than the \citet{lallement_threedimensional_2018}
value by a factor of two.  } Follow-up studies of the LDB or
main-sequence turn-off in the \cn\ could help determine a more precise
and accurate age for the cluster, however these are beyond our scope.

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{kounkel_untangling_2019}, \nwithtess\ stars were amenable to
rotation period measurements ($G<17$ and $\bpmrpo>0.5$) using the TESS
full frame image data.\footnote{Kepler rotation periods were derived
by \citet{mcquillan_rotation_2014} for 28 stars; for these cases, we
adopted the Kepler rotation period.  } We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (1 TESS pixel).  We recorded the
number of stars within the aperture with greater brightness than the
target star, and with brightness within 1.25 and 2.5 TESS magnitudes
of the target star.

We cleaned the candidate TESS rotation period measurements through a
combination of automated and manual steps.  As a matter of scope, we
restricted our attention to the \nkinwithtess\ stars discussed in
Appendix~\ref{app:kinematicselection} in the spatial and kinematic
proximity of Kepler\,1627.  To avoid blending, we also only focused on
stars for which no companions were known with a brightness exceeding
one-tenth of the target star in a $21\farcs0$ radius.  There were
\nkinwithtessandcrowding\ stars that met these requirements, and that
had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

@@

The second line of confirmatory evidence comes by analyzing the
individual Kepler transit times. We isolated each of the 144 observed
transits to within $\pm4.5$\,hr of each transit, and fitted each
window with both {\it i)} a local second-order polynomial and transit,
and {\it ii)} a local linear trend.  We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation (TTV), is plotted in Figure~\ref{fig:obliquity}
against the local linear slope.  A significant correlation of $-0.0564
\pm 0.0098\ {\rm ppt\,day}^{-1}$ is observed.  Fewer than ten Kepler
Objects of Interest have shown this correlation
\citep{holczer_time_2015}, which is most readily interpreted as a TTV
induced by unresolved starspot crossings \citep{mazeh_time_2015}.
This is only possible if the planet transits the primary star, which
excludes a background eclipsing binary scenario, and therefore
confirms that \pn\ is a planet.  It also suggests that the planet's
orbit is prograde.  The latter point assumes that the dominant
photometric variability is induced by dark spots, and not bright
faculae.  Given the observed transition of Sun-like stellar
variability from spot to faculae-dominated regimes between young and
old ages, we expect this assumption to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

A third supporting line of evidence for the planetary interpretation
also exists, though we consider it less definitive than the stellar
density and TTV-local slope correlation.  We observed a transit of
\pn\ on the night of 2021 Aug 7 simultaneously with Keck/HIRES and
MuSCAT3.  We scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit (Figure~\ref{fig:obliquity}, lower panels).  Fitting
the MuSCAT3 photometry with a model that lets the transit depths vary
across each bandpass, we find {\it griz} depths consistent with the
Kepler depth at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  The
MuSCAT3 observations also suggest a transit duration $17.4\pm3.6\ {\rm
minutes}$ shorter than the Kepler transits; further photometric
follow-up could help confirm whether the transit duration is indeed
changing.  For our RM analysis, the details are discussed in
Appendix~\ref{app:rm}.  While the velocities are marginally more
consistent with a prograde or polar orbit than a retrograde orbit, the
spot-corrected exposure-to-exposure scatter ($\sigma_{\rm RV}\approx
50$\ms) is larger than the expected velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$).  We are therefore
not in a position to claim a spectroscopic detection of the RM effect,
nor to quantify the stellar obliquity.

@@

Ultimately, the main advance of this work is a precise measurement of
the age of \pn.   This measurement was enabled by identifying the
connection of the star to the \cn\ using Gaia kinematics, and then by
using the Gaia HR diagram and TESS stellar rotation periods to verify the
cluster's existence.
Table~\ref{tab:v06} should enable similar cross-matches to already
known planets, as well as forthcoming planets from TESS
\citep{guerrero_tess_2021}.  An alternative
approach for age-dating more planets could be to identify kinematic
associations around known exoplanet host stars using positions and
tangential velocities from Gaia, and to then verify these associations
with ancillary rotation periods and spectroscopy \citep[{\it
e.g.},][]{tofflemire_tess_2021}.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic position and tangential velocities of the
    $\delta$\,Lyr cluster.}
    Points are candidate cluster members with $\varpi/\sigma_\varpi >
    20$, reported to be in the group by
    \citet{kounkel_untangling_2019}.  We focus on stars in a small
    region (black points) in the kinematic vicinity of Kepler\,1627
    (yellow star).  The other candidate cluster members (gray points)
    may or may not share the ages of the selected kinematic group.
    The location of the Sun is ($\odot$) is shown.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

Figure~\ref{fig:lc} shows the resulting model in orange (top) and
purple (bottom).  While the fit appears reasonably good, an asymmetry
is present during the transit: the measured flux is systematically
high during the first half, and low in the second half.  
To determine
whether this effect was caused by our stellar variability model, we 
explored an alternative approach in which we isolated each transit
window and locally fitted out polynomial trends, and then binned all
the observed transits; the asymmetry was still present, at a
comparable amplitude.
An important note is that even though this asymmetric feature is
within the plotted 2-$\sigma$ model uncertainties, this is within a
model that has a jitter term that grows to account for otherwise unmodelled 
white noise in the flux.
The significance of the asymmetry is therefore better assessed in
comparison against the intrinsic out-of-transit scatter, rather than the
model uncertainties.

>>>>

%\suppressAffiliations
%\NewPageAfterKeywords
\input{authors.tex}

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.4\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge,
  Kepler\,1627Ab is the youngest planet with a precise age yet found
  by the main Kepler mission.  The Kepler photometry shows two notable
  anomalies: the average Kepler transit profile appears to be
  asymmetric, and the individual transits show a correlation between
  the transit time and the local light curve slope.
  % The former could be explained by a dusty atmospheric outflow; the
  % latter could be explained by unresolved starspot crossings of a
  % planet on a prograde orbit.  
  We discuss plausible explanations for the light curve anomalies, and
  also highlight broader implications for our ability to expand the census
  of age-dated planets.
\end{abstract}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler's view of the $\delta$~Lyr cluster.} Each black circle is a
    candidate cluster member, selected from the catalog of \citet{KounkelCovey2019} based on its
    position and kinematics.
    Of the \nkinematic\ candidate cluster members, 58 have at least one
    quarter of Kepler data.  TESS has also observed most of the
    cluster, for one to two lunar months to date.
		\label{fig:skychart}
	}
\end{figure}

Matching our young star list against stars observed by Kepler yielded
%two discoveries.  The first, to be discussed in an upcoming analysis
%by J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr
%open cluster Theia~520 (UBC~1).  At least six Kepler planets are known
%in the cluster from the Kepler-52 and Kepler-968 systems
%\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
%discovery, and the focus of this work, is
the discovery that Kepler observed a portion of the \cn\ (Stephenson-1; Theia~73; \citealt{stephenson_possible_1959}).
Figure~\ref{fig:skychart} shows the overlap between the Kepler field
and the cluster.  A previous clustering analysis of the Gaia
data by \citet{kounkel_untangling_2019}
reported that Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a
member of the \cn.  Given the
previous statistical validation of the close-in mini-Neptune Kepler
1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and that \sn\ is indeed a member of the
cluster.  Focusing on the planet itself, we confirm that despite the
presence of a previously unreported binary companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A
(Section~\ref{sec:planet}).  Based on a correlation between the
planetary transit times and the local light curve slope, the orbit
also seems to be prograde.  We conclude by highlighting broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f2c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is \clusterage\ old.}  {\it Top:} Color-absolute
    magnitude diagram of candidate \cn\ members, in addition to stars
    in IC\,2602 ($\approx38$\,Myr), the Pleiades ($\approx 115$\,Myr),
    and the Gaia EDR3 Catalog of Nearby Stars (gray background).  The
    zoomed right panel highlights the pre-main-sequence.  The \cn\ and
    IC\,2602 are approximately the same isochronal age.  {\it Bottom:}
    TESS and Kepler stellar rotation period versus dereddened Gaia
    color, with the Pleiades and Praesepe (650\,Myr) shown for
    reference \citep{rebull_rotation_2016a,douglas_poking_2017}.  Most
    candidate \cn\ members are gyrochronally younger than the Pleiades; outliers are
    probably field interlopers.
   \label{fig:age}
	}
\end{figure*}

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades \citep{dahm_2015},
and a 16\,Myr age for UCL \citep{pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements 
\citep{dobbie_ic_2010,randich_gaiaeso_2018}
and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse extreme of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age for IC\,2602, which yields an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST isochrone
models over a grid of ages, metallicities, and reddenings, yielded the
best agreement for this $\approx 38\,$Myr age as well, given ${\rm
[Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CAMD
reddening is higher than the \citet{lallement_threedimensional_2018}
value by a factor of two.  } Follow-up studies of the LDB or
main-sequence turn-off in the \cn\ could help determine a more precise
and accurate age for the cluster, however these are beyond our scope.

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{kounkel_untangling_2019}, \nwithtess\ stars were amenable to
rotation period measurements ($G<17$ and $\bpmrpo>0.5$) using the TESS
full frame image data.\footnote{Kepler rotation periods were derived
by \citet{mcquillan_rotation_2014} for 28 stars; for these cases, we
adopted the Kepler rotation period.  } We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (a radius of 1 TESS pixel).
Within this radius, we recorded the number of stars with greater
brightness than the target star, and with brightness within 1.25 and
2.5 TESS magnitudes of the target star.

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.  As a matter of
scope, we restricted our attention to the \nkinwithtess\ stars
discussed in Appendix~\ref{app:kinematicselection} in the spatial and
kinematic proximity of Kepler\,1627.  To avoid blending, we also only
focused on stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

@@

The second line of confirming evidence comes by analyzing the
individual Kepler transit times. We isolated each of the 144 observed
transits to within $\pm4.5$\,hr of each transit, and fitted each
window with both {\it i)} a local second-order polynomial and transit,
and {\it ii)} a local linear trend.  We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation (TTV), is plotted in Figure~\ref{fig:obliquity}
against the local linear slope.  A significant correlation of $-0.0564
\pm 0.0098\ {\rm ppt\,day}^{-1}$ is observed.  Fewer than ten Kepler
Objects of Interest have shown this correlation
\citep{holczer_time_2015}, which is most readily interpreted as a TTV
induced by unresolved starspot crossings \citep{mazeh_time_2015}.
This is only possible if the planet transits the primary star, which
excludes a background eclipsing binary scenario, and therefore
confirms that \pn\ is a planet.  It also suggests that the planet's
orbit is prograde.  The latter point assumes that the dominant
photometric variability is induced by dark spots, and not bright
faculae.  Given the observed transition of Sun-like stellar
variability from spot to faculae-dominated regimes between young and
old ages, we expect this assumption to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

A third supporting line of evidence for the planetary interpretation
exists, though we consider it less definitive than the stellar
density and TTV-local slope correlation.  We observed a transit of
\pn\ on the night of 2021 Aug 7 simultaneously with Keck/HIRES and
MuSCAT3.  We scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit (Figure~\ref{fig:obliquity}, lower panels).  Fitting
the MuSCAT3 photometry with a model that lets the transit depths vary
across each bandpass, we find {\it griz} depths consistent with the
Kepler depth at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  The
MuSCAT3 observations also suggest a transit duration $17.4\pm3.6\ {\rm
minutes}$ shorter than the Kepler transits; further photometric
follow-up could help confirm whether the transit duration is indeed
changing.  For our RM analysis, the details are discussed in
Appendix~\ref{app:rm}.  While the velocities are marginally more
consistent with a prograde or polar orbit than a retrograde orbit, the
spot-corrected exposure-to-exposure scatter ($\sigma_{\rm RV}\approx
50$\ms) is larger than the expected velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$).  We are therefore
not in a position to claim a spectroscopic detection of the RM effect,
nor to quantify the stellar obliquity.

@@

Ultimately, the main advance of this work is a precise measurement of
the age of \pn.   This measurement was enabled by identifying the
connection of the star to the \cn\ using Gaia kinematics, and then by
using the Gaia HR diagram and TESS stellar rotation periods to verify
the cluster's existence.  Table~\ref{tab:v06} enables similar
cross-matches for both known and forthcoming exoplanet
systems \citep[{\it e.g.},][]{guerrero_tess_2021}.  The entry shown in
the header of Table~\ref{tab:v06}, HD 150706b, is an example: the
host star appears to be a member of the Ursa Major moving group
($\approx 400\,{\rm Myr}$; \citealt{mann_tess_2020}).  Confirming
such kinematic associations with independent age indicators is
essential, because the false positive rates are uncharted.
Alternatively, one could instead opt to identify new kinematic
associations around known exoplanet host stars using positions and
tangential velocities from Gaia, and to then verify these associations
with stellar rotation periods and spectroscopy \citep[{\it
e.g.},][]{tofflemire_tess_2021}.  
Each path seems likely to expand the census of planets with precisely
measured ages over the coming years.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic position and tangential velocities of the
    $\delta$\,Lyr cluster.}
    Points are candidate cluster members with $\varpi/\sigma_\varpi >
    20$, reported to be in the group by
    \citet{kounkel_untangling_2019}.  We focus on stars (black points)
    in the spatial and kinematic vicinity of Kepler\,1627 (yellow
    star).  The other candidate cluster members (gray points) may or
    may not share the ages of the selected kinematic group.  The
    location of the Sun is ($\odot$) is shown.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

Figure~\ref{fig:lc} shows the resulting model in orange (top) and
purple (bottom).  While the fit appears reasonably good, an asymmetry
is present during the transit: the measured flux is systematically
high during the first half, and low in the second half.  The
semi-amplitude of the deviation is $\approx50\,{\rm ppm}$, which
represents a $\approx 3\%$ distortion of the transit depth
($\approx1700\,{\rm ppm}$).  To determine whether this effect was
caused by our stellar variability model, we explored an alternative
approach in which we isolated each transit window and locally fitted
out polynomial trends, and then binned all the observed transits; the
asymmetry was still present, at a comparable amplitude.  Note that
even though this asymmetric feature is within the 2-$\sigma$ model
uncertainties, this model itself has a jitter term that grows to
account for otherwise unmodelled white noise in the flux.  The
significance of the asymmetry is therefore best assessed in comparison
against the intrinsic out-of-transit scatter, not the model
uncertainties.
